\documentclass[10pt]{article}
\usepackage{fontspec} 
\setmainfont{Lato}[Extension = .ttf,UprightFont = *-Regular, BoldFont = *-Bold, SmallCapsFont = *-Light, ItalicFont = *-Italic]
\usepackage{calc}
\usepackage[english, greek]{babel}

\makeatletter
\newlength{\bibhang}
\setlength{\bibhang}{1em}
\newlength{\bibsep}
 {\@listi \global\bibsep\itemsep \global\advance\bibsep by\parsep}
\newenvironment{bibsection}
    {\minipage[t]{\linewidth}\list{}{%
        \setlength{\leftmargin}{\bibhang}%
        \setlength{\itemindent}{-\leftmargin}%
        \setlength{\itemsep}{\bibsep}%
        \setlength{\parsep}{\z@}%
        }}
    {\endlist\endminipage}
\makeatother

% Layout: Puts the section titles on left side of page
\reversemarginpar

\usepackage[paper=a4paper,
           includefoot, % Uncomment to put page number above margin
           marginparwidth=30.5mm,    % Length of section titles
           marginparsep=1.5mm,       % Space between titles and text
           margin=25mm,              % 25mm margins
           includemp]{geometry}

%% More layout: Get rid of indenting throughout entire document
\setlength{\parindent}{0in}

%% This gives us fun enumeration environments. compactitem will be nice.
\usepackage{paralist}

%% Reference the last page in the page number
%
% NOTE: comment the +LP line and uncomment the -LP line to have page
%       numbers without the ``of ##'' last page reference)
%
% NOTE: uncomment the \pagestyle{empty} line to get rid of all page
%       numbers (make sure includefoot is commented out above)
%
\usepackage{fancyhdr,lastpage}
\pagestyle{fancy}
\pagestyle{empty}      % Uncomment this to get rid of page numbers
\fancyhf{}\renewcommand{\headrulewidth}{0pt}
\fancyfootoffset{\marginparsep+\marginparwidth}
\newlength{\footpageshift}
\setlength{\footpageshift}
          {0.5\textwidth+0.5\marginparsep+0.5\marginparwidth-2in}
\lfoot{\hspace{\footpageshift}%
       \parbox{4in}{\, \hfill %
                    \arabic{page} of \protect\pageref*{LastPage} % +LP
%                    \arabic{page}                               % -LP
                    \hfill \,}}

% Finally, give us PDF bookmarks
\usepackage{color,hyperref}
\usepackage[dvipsnames]{xcolor}
\definecolor{darkblue}{HTML}{9B0E0E}


\hypersetup{colorlinks,breaklinks,
            linkcolor=darkblue,urlcolor=darkblue,
            anchorcolor=darkblue,citecolor=darkblue,
            }


\usepackage{anyfontsize}
% The title (name) with a horizontal rule under it
%
% Usage: \makeheading{name}
%
% Place at top of document. It should be the first thing.
\newcommand{\makeheading}[1]{
\begin{center}\hspace{-16mm}{\fontsize{35}{60}{\selectfont{\scshape#1}}}\end{center}
\vspace{10pt}
}

\renewcommand{\section}[2]%
        {\pagebreak[2]\vspace{1.3\baselineskip}%
         \phantomsection\addcontentsline{toc}{section}{#1}%
         \hspace{0in}%
         \marginpar{
         \raggedright \
         
         \scshape #1}#2}

% An itemize-style list with lots of space between items
\newenvironment{outerlist}[1][\enskip\textbullet]%
        {\begin{itemize}[#1]}{\end{itemize}%
         \vspace{-.6\baselineskip}}

% An environment IDENTICAL to outerlist that has better pre-list spacing
% when used as the first thing in a \section
\newenvironment{lonelist}[1][\enskip\textbullet]%
        {\vspace{-\baselineskip}\begin{list}{#1}{%
        \setlength{\partopsep}{0pt}%
        \setlength{\topsep}{0pt}}}
        {\end{list}\vspace{-.6\baselineskip}}

% An itemize-style list with little space between items
\newenvironment{innerlist}[1][\enskip\textbullet]%
        {\begin{compactitem}[#1]}{\end{compactitem}}

\newcommand{\blankline}{\quad\pagebreak[2]}

% 

\usepackage{eurosym}

\begin{document}\latintext
\makeheading{Olivia Guest}


\section{CONTACT}

\begin{minipage}{.49\textwidth}
\begin{description}
 \item [Phone:] +44 7842 868199 (UK)
 \item[Email:] \href{mailto:contact@oliviaguest.com}{contact@oliviaguest.com}
 \item[Website:] \href{http://oliviaguest.com}{oliviaguest.com}
% \item[Address:] South Parks Rd, OX1 3UD
 \end{description}
\end{minipage}
\begin{minipage}{.49\textwidth}
\begin{description}
 \item[GitHub:] \href{https://github.com/oliviaguest}{oliviaguest}
 \item[Twitter:] \href{https://twitter.com/o_guest}{@o\textunderscore guest}
% \item[OSF:] \href{https://osf.io/38p75/}{Olivia Guest}
 \item[ORCID:] \href{http://orcid.org/0000-0002-1891-0972}{0000-0002-1891-0972}
 \end{description}
\end{minipage}
\vspace{10pt}

\section{PROFESSIONAL EXPERIENCE}

\textbf{\href{http://rescience.github.io/}{ReScience Journal}} --- \textit{Associate Editor} \hfill \textbf{2016--}
\vspace{10pt}

\textbf{\href{http://www.software.ac.uk/}{Software Sustainability Institute}, UK} ---  \textit{Fellow 2016}  \hfill \textbf{2016--}
\vspace{10pt}

\textbf{\href{https://www.ucl.ac.uk/pals/research/experimental-psychology/}{Department of Experimental Psychology}, University College London, UK}
\begin{outerlist}
\item[\textit{Postdoctoral Researcher}] \hfill \textbf{2016--}
\end{outerlist}
\vspace{10pt}

\textbf{\href{http://www.psy.ox.ac.uk/}{Department of Experimental Psychology}, University of Oxford, UK}
\begin{outerlist}
\item[\textit{Postdoctoral Researcher}] \hfill \textbf{2014--2016}

\begin{innerlist}
\item Created models for category learning in infancy.
\item Tutored on the Language and Cognition module.
\item Ran and developed the Block Practical: \href{http://oliviaguest.com/connectionism}{Connectionist Models and Cognitive Processes}.
\end{innerlist}
\end{outerlist}
\vspace{10pt}

\textbf{\href{http://www.bbk.ac.uk/psychology/}{Department of Psychological Sciences}, \href{http://www.bbk.ac.uk/}{Birkbeck}, UK}
\begin{outerlist}
\item[\textit{Graduate Teaching Assistant}] \hfill \textbf{2010--2014}

\begin{innerlist}
\item Taught on a range of courses within psychological sciences.
\item Was trained to evaluate, mark, invigilate, and support part-time, mature, and full-time students.
\item Managed the SONA system.
\item Organised and led the \href{http://cccm.bbk.ac.uk/}{Centre for Cognition, Computation and Modelling}'s  seminar. 
\end{innerlist}
\end{outerlist}

\section{PUBLICATIONS}

\textbf{Guest, O.}, Caso, A., Cooper, R. P. (in prep). On Simulating Neural Damage in Connectionist Networks.
\vspace{5pt}

\textbf{Guest, O.}, Love, B. C. (2017). \href{http://dx.d.oi.org/10.7554/eLife.21397}{What the Success of Brain Imaging Implies about the Neural Code}. \textit{eLife}, 6:e21397.
\vspace{5pt}

\textbf{Guest, O.}, Rougier, N. P. (2016). \href{http://oliviaguest.com/doc/guest_rougier_16.pdf}{What is computational reproducibility?} \textit{IEEE CIS Newsletter on Cognitive and Developmental Systems}, 13 (1).
\vspace{5pt}

\textbf{Guest, O.} (2016). \href{http://dx.doi.org/10.15200/winn.146590.01538}{Crisis in What Exactly?}. \textit{The Winnower}. 
\vspace{5pt}

Love, B. C., Kopeć, Ł., \textbf{Guest, O.} (2015). \href{http://dx.doi.org/10.1371/journal.pone.0137685}{Optimism Bias in Fans and Sports Reporters}. \textit{PLoS ONE}, 10 (9).
\vspace{5pt}

Cooper, R. P., \textbf{Guest, O.} (2014).  \href{http://dx.doi.org/10.1016/j.cogsys.2013.05.001}{Implementations are not specifications: specification, replication and experimentation in computational cognitive modeling}. \textit{Cognitive Systems Research}, 27, 42--49.
\vspace{5pt}

\textbf{Guest, O.}, Cooper, R. P., Davelaar, E. J. (2014).  [High-Level Cognition]. \href{http://oliviaguest.com/doc/guest_14.pdf}{The Influence of Implementation on ``Hub'' Models of Semantic Cognition}. In J. Mayor, P. Gomez (Eds.), \textit{\href{http://www.worldscientific.com/worldscibooks/10.1142/8747}{Computational Models of Cognitive Processes}} (pp. 155--169). World Scientific.
\vspace{5pt}

\textbf{Guest, O.}, Cooper, R. P., Davelaar, E. J. (2012). \href{http://eprints.bbk.ac.uk/6758/}{Semantic Cognition: A Re-examination of the Recurrent Network ``Hub'' Model}. \textit{In Proceedings of the Ninth International Conference on Cognitive Modelling.} Berlin, Germany. April. (pp. 259--264). Berlin, Germany. April. Universit\"{a}tsverlag der TU Berlin.

\section{EDUCATION}

\textbf{\href{http://www.bbk.ac.uk/}{Birkbeck}, UK} \hfill \textbf{2010--2014}
\begin{outerlist}
 \item[Ph.D., Psychological Sciences,] Sep 2014
        \begin{innerlist}
        \item Thesis: \emph{Towards a Unified Computational Account of Semantic Impairments}
	    \item Primary Supervisor: \emph{Prof. Richard P. Cooper}
        \item Secondary Supervisor: \emph{Dr. Eddy J. Davelaar}
        \end{innerlist}
\end{outerlist}
\vspace{10pt}

\textbf{\href{http://www.ucl.ac.uk/}{University College London}, UK} \hfill \textbf{2009--2010}
\begin{outerlist}
 \item[M.Sc., \href{http://www.ucl.ac.uk/lifesciences-faculty/degree-programmes/cognitive-decision-sciences}{Cognitive and Decision Sciences} (Distinction),] Sep 2010
        \begin{innerlist}
        \item Thesis: \emph{Modelling Semantic Memory \& Its Impairments Following Neural Damage}
	\item Supervisor: \emph{Prof. Richard P. Cooper}
        \end{innerlist}
\end{outerlist}
\vspace{10pt}

\textbf{\href{http://www.york.ac.uk/}{The University of York}, UK} \hfill \textbf{2006--2009}
\begin{outerlist}
\item[B.Sc., \href{http://www.cs.york.ac.uk/} {Computer Science},] Jun 2009
\end{outerlist}

\section{CONFERENCES}

\textbf{\href{http://www.cogs.indiana.edu/asic/2016/index.shtml}{15th Annual Summer Interdisciplinary Conference (ASIC 2016)}}
\begin{outerlist}
\item[] \textit{Selva, Val Gardena, Italy}\hfill\textbf{3--8 Jul 2016}
\begin{innerlist}
\item Talk: \textit{What the Success of Brain Imaging Implies about the Neural Code}.
\end{innerlist}
\end{outerlist}
\vspace{10pt}

\textbf{\href{http://www.cogs.indiana.edu/asic/2015/index.shtml}{14th Annual Summer Interdisciplinary Conference (ASIC 2015)}}
\begin{outerlist}
\item[] \textit{Mammoth Lakes, California, USA}\hfill\textbf{10--15 Jul 2015}
\begin{innerlist}
\item Talk: \textit{Optimism Bias in Novice and Expert Sport Forecasting}.
\end{innerlist}
\end{outerlist}
\vspace{10pt}

\textbf{\href{http://www.bcbl.eu/events/ncpw13/}{13th Neural Computation and Psychology Workshop (NCPW 13)}}
\begin{outerlist}
\item[] \textit{\href{http://www.bcbl.eu/}{BCBL}, San Sebastian, Spain}\hfill\textbf{12--14 Jul 2012}
\begin{innerlist}
\item Talk: \textit{Exploring the influence of architecture and learning algorithm on the breakdown of the ``hub'' model of semantic cognition}.
\end{innerlist}
\end{outerlist}
\vspace{10pt}

\textbf{\href{http://iccm-conference.org/2012/}{11th International Conference on Cognitive Modeling (ICCM 2012)}}
\begin{outerlist}
\item[] \textit{\href{http://www.tu-berlin.de/menue/home/parameter/en/}{Technische Universit\"{a}t Berlin}, Berlin, Germany}
        \hfill \textbf{12--15 Apr 2012}
\begin{innerlist}
\item Poster: \textit{Semantic Cognition: A Re-examination of the Recurrent Network ``Hub'' Model}.
\item Won best student poster prize (\euro 100).
\end{innerlist}
\end{outerlist}

\section{WORKSHOPS}

\textbf{\href{http://www.software.ac.uk/rdvw/}{Research Data Visualisation Workshop (RDVW)}}
\begin{outerlist}
\item[] \textit{\href{http://software.ac.uk/}{Software Sustainability Institute}, \href{http://www.manchester.ac.uk/}{University of Manchester}} \hfill \textbf{28 Jul 2016}
\begin{innerlist}
 \item Organised 1-day workshop with \href{http://www.software.ac.uk/about/people/raniere-silva}{Raniere Silva} (main organiser) and \href{http://www.cardiff.ac.uk/people/view/98654-knight-vincent}{Vince Knight}.
 \item Member of \href{http://www.software.ac.uk/rdvw/committees}{steering committee}.
 \item Obtained funding from \href{https://www.rstudio.com/}{RStudio}.
\end{innerlist}
\end{outerlist}
\vspace{10pt}

\textbf{\href{https://sites.google.com/site/introcompcog/}{Introduction to Computational Cognitive Modelling Workshop}}
\begin{outerlist}
\item[] \textit{\href{http://cccm.bbk.ac.uk/}{CCCM}, Birkbeck}         \hfill \textbf{23--25 Apr 2014}
\begin{innerlist}
 \item Organised 3-day workshop with \href{https://www.researchgate.net/profile/Chris_Brand}{Chris Brand} (co-organiser).
 \item Prepared slides, exercises, created website.
\end{innerlist}
\end{outerlist}

\section{TEACHING}

\textbf{\href{http://www.psy.ox.ac.uk/}{Department of Experimental Psychology}, \href{http://ox.ac.uk/}{University of Oxford}, UK}
  \begin{outerlist}
  \item[Postdoctoral Research Assistant] \hfill \textbf{2014--}
  \item[\textit{\href{http://oliviaguest.com/connectionism}{Block Practical: Connectionist Models and Cognitive Processes}}] \
  \begin{innerlist}
  \item Module: \textit{Third Year, B.Sc.}
   \item Designed course structure and materials (slides and exercises).
   \item Set final report wherein students replicated from scratch Tyler et al. (2000) in Python.
   \item Created course website: \href{http://oliviaguest.com/connectionism}{oliviaguest.com/connectionism}.
  \end{innerlist}
  \item[\textit{Tutorial: Language and Cognition}] \
  \begin{innerlist}
  \item Module: \textit{Second Year, B.Sc.}
   \item Set essays and marked exams.
  \end{innerlist}
  \end{outerlist}
\vspace{10pt}

\textbf{\href{http://www.bbk.ac.uk/psychology/}{Department of Psychological Sciences}, \href{http://www.bbk.ac.uk/}{Birkbeck, University of London},
UK}
\begin{outerlist}
 \item[Graduate Teaching Assistant] \hfill \textbf{2010--2014}
 \item Modules Taught: \textit{General Foundations of Psychology,
 Psychobiology, Advanced Research Methods, Advanced Quantitative Methods, Memory and Cognition, Matlab Programming for Psychological Science, }
\end{outerlist}

\section{MEDIA OUTREACH}

\textbf{\href{http://www.bbc.co.uk/radio4}{BBC Radio 4:}} \href{http://www.bbc.co.uk/programmes/b0713zdz}{Today Show} \hfill\textbf{22 Feb 2016}
\begin{innerlist}
\item Interview: \textit{What can we learn in 4 months?}
\end{innerlist}
\vspace{10pt}

\textbf{\href{http://journals.plos.org/plosone/article?id=10.1371/journal.pone.0137685}{Optimism Bias in Fans and Sports Reporters}} \hfill\textbf{9 Sep 2015}
\begin{innerlist}
\item Press Releases: \href{http://www.ox.ac.uk/news/2015-09-09-nfl-fans-and-espn-reporters-overly-optimistic-about-team-prospects}{University of Oxford}, \href{https://www.ucl.ac.uk/news/news-articles/0915/100915-nfl-team-prospects}{UCL}
\item Media Coverage: \href{http://www.csmonitor.com/Science/2015/0909/NFL-scores-Your-team-is-probably-less-invincible-than-you-imagine}{CS Monitor},
\href{http://www.medicaldaily.com/rose-colored-glasses-nfl-fans-and-sports-reporters-overestimate-how-good-their-teams-351888}{Medical Daily},
\href{https://www.minnpost.com/second-opinion/2015/09/why-football-fans-are-unrealistically-optimistic-and-why-it-matters}{MinnPost},
\href{http://europe.newsweek.com/nfl-fans-and-reporters-overly-optimistic-about-teams-prospects-332758}{Newsweek},
\href{http://www.psmag.com/health-and-behavior/this-study-explains-why-raiders-fans-continue-going-to-watch-their-team-play}{Pacific Standard},
\href{http://phys.org/news/2015-09-nfl-fans-espn-overly-optimistic.html}{Phys.org}. 
\end{innerlist}

\section{TECHNICAL SKILLS}

\textbf{General:} \href{http://oliviaguest.com/license/}{Website design} (HTML, CSS, CMS, Jekyll, Liquid, YAML); Graphic design (Adobe CS); GUI design (PyGTK, GTK+); Artificial neural networks (e.g., TensorFlow); Unix administration (e.g., command line, LAMP web server), Eye-tracking (data collection and analysis).
\vspace{10pt}

% Adapted from http://tex.stackexchange.com/a/4304/9668
\newcommand{\CC}{C\nolinebreak\hspace{.02em}+\nolinebreak\hspace{0.04em}+}

\textbf{Programming:} Ada, C, \CC, C\#, Java, JavaScript, \LaTeX, MATLAB,  OpenGL, Pascal, PHP, Prolog, Python, R, Scheme, SQL, Visual Basic.

\end{document}
%%%%%%%%%%%%%%%%%%%%%%%%%% End CV Document %%%%%%%%%%%%%%%%%%%%%%%%%%%%%
